Yeast General Read Sequence Figure Generation

### 2022-06-01 R/YeastDeaminationAnchoredExcisionSiteDataGeneration.rmd
Added yeast notebooks

---
title: "XP-C Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 10
cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

>>>>

---
title: "Yeast Deamination Anchored Excision Site Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 10
cellType = "yeast"
CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
minReadLength = 22; maxReadLength = 25

### 2022-06-01 R/YeastDeaminationAnchoredExcisionSiteFigureGeneration.rmd
Added yeast notebooks

---
title: "XP-C Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

>>>>

---
title: "Yeast Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

### 2022-06-01 R/YeastDeaminationSequenceAndPositionDataGeneration.rmd
Added yeast notebooks

---
title: "XP-C Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 0
cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

>>>>

---
title: "Yeast Deamination Sequence and Position Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

expansionOffset = 0
cellType = "yeast"
CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
minReadLength = 22; maxReadLength = 25

### 2022-06-01 R/YeastDeaminationSequenceAndPositionFigureGeneration.rmd
Added yeast notebooks

---
title: "XP-C Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
minReadLength = 22; maxReadLength = 30

>>>>

---
title: "Yeast Deamination Sequence and Position Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

cellType = "yeast"
CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
minReadLength = 22; maxReadLength = 25

### 2022-06-01 R/YeastGeneralReadSequenceDataGeneration.rmd
Added yeast notebooks

---
title: "XP-C General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

>>>>

---
title: "Yeast General Read Sequence Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

### 2022-06-01 R/YeastGeneralReadSequenceFigureGeneration.rmd
Added yeast notebooks

---
title: "XP-C General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

>>>>

---
title: "Yeast General Read Sequence Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---
